Investigating the outer reaches of the Sculptor and Ursa Minor dwarf galaxies

### 2025-07-25 thesis/introduction.tex
more introduction updates

Dwarf galaxies span a large range of physical sizes, luminosities, and
morphologies. Broadly, there are three classes of dwarf galaxies based
on luminosity, as illustrated by Fig.~\ref{fig:galaxy_images}. Local
\textbf{bright dwarfs galaxies} with magnitudes
\(-18 \lesssim M_V \lesssim  -14\), often exhibit irregular morphologies
and recent star formation. Fig.~\ref{fig:galaxy_images} shows the LMC as
an example of an irregular (and slightly bright) dwarf galaxy displaying
a bar. \textbf{Classical dwarf} galaxies occupy intermediate
luminosities ( \(-14 \lesssim M_V  \lesssim -7.7\)). Typically, these
systems are old, gas-poor, and spheroidal. All Milky Way satellites
discovered before digital sky surveys are classicals. The 12 classical
dwarfs satellites of our galaxy are Sagittarius, Fornax, Leo I,
Sculptor, Antlia II, Leo II, Carina, Draco, Ursa Minor, Canes Venatici
I, Sextans I, and Crater II.\footnote{While formally the dwarf galaxy
  names we discuss contain'' dwarf spheroidal'' (dSph), e.g.~Sculptor
  dSph, we omit this suffix for brevity.} The ultra-faints occupy the
very faintest magnitudes (\(-7.7 \lesssim M_V\)). These galaxies have
miniscule stellar masses, tend to be more compact, and are the darkest
known galaxies. An example is Boötes V as shown in
Fig.~\ref{fig:galaxy_images}. Altogether, dwarf galaxies span about 7
orders of magnitude in stellar mass.

@@

\emph{Gaia} has revolutionized many fields of astronomy including the
Milky Way and the Local Group. For example, 6D kinematic classification
of Milky Way stars has lead to the discovery of past mergers or Milky
Way building blocks like \emph{Gaia}-sausage Enceladus
\citep[e.g.,][]{helmi+2018}, out-of-equilibrium structures like the
\emph{Gaia} snail {[}e.g., \citet{antoja+2018l}, and effects of the
Milky Way's bulge and bar \citep{hunt+vasiliev2025}. Moving to the Milky
Way halo, numerous streams \citep{bonaca+price-whelan2025}. \emph{Gaia}
has revealed the hierarchical formation and messy structure of our own
galaxy.

>>>>

Dwarf galaxies span a large range of physical sizes, luminosities, and
morphologies. Broadly, there are three classes of dwarf galaxies based
on luminosity, as illustrated by Fig.~\ref{fig:galaxy_images}. Local
\textbf{bright dwarfs galaxies} with magnitudes
\(-18 \lesssim M_V \lesssim  -14\), often exhibit irregular morphologies
and recent star formation. Fig.~\ref{fig:galaxy_images} shows the LMC as
an example of an irregular (and slightly bright) dwarf galaxy displaying
a bar. \textbf{Classical dwarf} galaxies occupy intermediate
luminosities ( \(-14 \lesssim M_V  \lesssim -7.7\)). Typically, these
systems are old, gas-poor, and spheroidal. All Milky Way satellites
discovered before digital sky surveys are classicals. The 12 classical
dwarfs satellites of our galaxy are Sagittarius, Fornax, Leo I,
Sculptor, Antlia II, Leo II, Carina, Draco, Ursa Minor, Canes Venatici
I, Sextans I, and Crater II.\footnote{While formally the dwarf galaxy
  names we discuss contain'' dwarf spheroidal'' (dSph), e.g.~Sculptor
  dSph, we omit this suffix for brevity.} The \textbf{ultra-faint}s
occupy the very faintest magnitudes (\(-7.7 \lesssim M_V\)). These
galaxies have minuscule stellar masses, tend to be more compact, and are
the darkest known galaxies. An example is Boötes V as shown in
Fig.~\ref{fig:galaxy_images}. Altogether, dwarf galaxies span about 7
orders of magnitude in stellar mass.

@@

\emph{Gaia} has revolutionized many fields of astronomy including the
Milky Way and the Local Group. For example, 6D kinematic classification
of Milky Way stars has lead to the discovery of past mergers or Milky
Way building blocks like \emph{Gaia}-sausage Enceladus
\citep[e.g.,][]{helmi+2018}, out-of-equilibrium structures like the
\emph{Gaia} snail {[}e.g., \citet{antoja+2018l}, and effects of the
Milky Way's bulge and bar \citep{hunt+vasiliev2025}. Moving to the Milky
Way halo, numerous streams \citep{bonaca+price-whelan2025}. \emph{Gaia}
has revealed the hierarchical formation and complex, evolving structure
of our own galaxy.
